GOmeth test

### 2023-09-14 figs/step_01b_test_gometh.Rmd
overlap

@@

@@

Find the overlap between mitch (competitive test) and ttest (self contained).

>>>>

head(sig[order(-abs(sig$t_median)),],30) %>%
  kbl(caption = "Top effect size genesets after FDR filtering") %>%
  kable_paper("hover", full_width = F)

@@

## Overlap

Use Euler diagrams to find the similarity.
As medians are normally distributed about the zero, one would expect equal numbers of up and down-
methylated gene sets.
Therefore the t-test based approach could be considered better.

```{r,ol1}

msig_up <- subset(msig,s.dist>0)$set
msig_dn <- subset(msig,s.dist<0)$set

tsig_up <- rownames(subset(tsig,t_median>0))
tsig_dn <- rownames(subset(tsig,t_median<0))

v1 <- list("mitch up"=msig_up, "mitch dn"=msig_dn,
  "ttest up"=tsig_up,"ttest dn"=tsig_dn)

plot(euler(v1),quantities = TRUE)

@@
